---
title: "p8105_hw5_yy3307"
output: github_document
date: "2022-11-03"
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(viridis)
library(purrr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r, message = FALSE}
full_df = 
  tibble(
    files = list.files("data/"),
    path = str_c("data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

First we need to import the `homicide` dataset and clean-up the variable names.

```{r, message = FALSE}
homicide_raw = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  janitor::clean_names()
```

To describe raw data, we need some basic inline R code to generate some info that we need.

```{r}
raw_row = nrow(homicide_raw)
raw_col = ncol(homicide_raw)
```

The raw homicide dataset has `r raw_row` rows and `r raw_col` columns, including main variables of `reported_date`, victims' information such as `name, age, race, gender`, reported `city` and its corresponding geographic location `lat, lon`, and cases' `disposition`.

Then we want to analyze total number of homicides and unsolved homicides in each city state. First we need to add a `city_state` variable as a combination of the `city` and `state`. Then we can group the data by  `city_state` and count for number of total homicide and unsolved homicide in each city state.

```{r, message = FALSE}
homicide_raw =
  homicide_raw %>% 
  mutate(
    city_state = str_c(city, ", ", state)
  )

homicide_count =
  homicide_raw %>%
  group_by(city_state) %>%
  summarize(
    total_homicide = n(),
    total_unsolved_homicide = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest")
  )

homicide_count
```

What we want next is to use `prop.test` function to estimate the proportion of unsolved homicides for `Baltimore, MD` and tidy it.

```{r}
Baltimore_summary = 
  homicide_count %>% 
  filter(city_state == "Baltimore, MD")


Baltimore_homicide =
  prop.test(
    Baltimore_summary %>% pull(total_unsolved_homicide), 
    Baltimore_summary %>% pull(total_homicide)
  ) %>% 
  broom::tidy()
```

We get the `estimated proportion` of unsolved homicides in Baltimore, MD is about `r Baltimore_homicide$estimate * 100`%, with a confidence interval from (`r Baltimore_homicide$conf.low * 100`%, `r Baltimore_homicide$conf.high * 100`%).

The we are going to expand the estimation proportion of unsolved homicides for all cities in the dataset. I'll use `map2` function to setup a nested tibble with the test statistics I wanted for each cities, and then use the `map` function to apply `broom:tidy` function to all tibbles. After `unnest` the tibbles, we can select the variables that we want to keep.

```{r}
cities_summary =
  homicide_count %>%
  mutate(
    cities_est = map2(.x = total_unsolved_homicide, .y = total_homicide, ~prop.test(.x, .y)),
    cities_est = map(.x = cities_est, ~broom::tidy(.x))
  ) %>% 
  unnest() %>%
  select(city_state, estimate, conf.low, conf.high)
```

We can use `fct_reorder` to reorganize cities according to the proportion of unsolved homicides. Then, we need to make a plot visualizing the estimations as `geom_point` and CI for each cities as `geom_errorbar`. 

```{r}
city_plot =
  cities_summary %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(
    title = "Unsolved Homicide Estimate Proportion with CI for Each City",
    y = "Unsolved Homicide Estimate Proportion",
    x = "City",
    caption = "Data from Washington Post"
  ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), plot.title = element_text(hjust = 0.5))

city_plot
```

## Problem 3

First we are going to set design elements with fixed n = 30 and fixed sigma = 5. We can create a function of the following t-distribution below.

```{r}
sim_mean_p = function(n = 30, mu, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(n = n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    t.test(mu = 0, alpha = 0.05, conf.level = 0.95) %>% 
    broom::tidy() %>%
    mutate(
      mu_hat = estimate,
      p_value = p.value
    ) %>% 
    select(mu_hat, p_value)
}
```

Then are are going to `rerun` the model function to generate 5000 datasets with mu = 0 and alpha = 0.05.

```{r}
sim_results_df = 
  rerun(5000, sim_mean_p(mu = 0)) %>% 
  bind_rows()

sim_results_df
```

We can also repeat the above with specific values of mu.

```{r}
sim_mu = 
  expand.grid(
    samp_mu = 1:6,
    iteration = 1:5000
  ) %>% 
  mutate(
    estimate_mu = map(.x = samp_mu, ~sim_mean_p(mu = .x))
  ) %>%
  unnest(estimate_mu)
```

